---
title: "Data Products Map Project"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## COVID Data

To create out interactive COVID map, we first download current COVID infrection data from

[Data Link](https://coronavirus-resources.esri.com/datasets/)

According to the website, their data is updated daily, and as can be seen from the dates in the resulting .csv file, most of the data is for 6 Feb 2021, which is the current date as this is written.  

## Load Data and Packages

- Load tidyverse for ease of manipulating data
- Load leaflet to create the interactive map
- Load the downloaded .csv file as a tibble

```{r}
suppressMessages(library(tidyverse))
suppressMessages(library(leaflet))

COVID <- tibble(read.csv("~/Desktop/COVID-19_Cases_US.csv"))
```

## Prepare the Data

- Filter out NA values for unassigned cases and non-US locations (mostly Puerto Rico)
- Create a column with county names along with the number of cases for marker popups
- Break number of cases into classes
- Color markers by number of cases

```{r}
COVID <- COVID %>% filter(!is.na(Lat)) %>% filter(!is.na(Long_)) %>% 
     filter(Country_Region == "US")
COVID <- COVID %>% mutate(PopupInfo=paste(Admin2,Confirmed,sep=", "))
COVID <- COVID %>% mutate(InfClass=cut(Confirmed,breaks=
     c(0,1000,10000,50000,500000)))
COVID <- COVID %>% mutate(MyColor=factor(InfClass,labels=
     c("blue","green","yellow","red")))
```

## Create the Map

- Create the map
- Add markers with popup information, clustering, and color by number of cases
- Add a legend

```{r}
MyMap <- COVID %>% leaflet() %>% addTiles() %>% 
     addCircleMarkers(lat=~Lat,lng=~Long_,popup=~PopupInfo,
     clusterOptions=markerClusterOptions(),color=~MyColor) %>%             
     addLegend(labels=c("low","moderate","medium","high"),
     colors=c("blue","green","yellow","red"))
```

## The Map

```{r,fig.cap="Cumulative COVID Infections on 6 Feb 2021"}
MyMap
```